Synthesizing Symmetric Lenses

### 2018-07-09 papers/SymmetricLenses/main.tex
Half an abstract -- will write more on it tomorrow if no one beats me to it

%% \bcp{This bit feels more detailed / technical than needed for an abstract.}
%%   We develop a type-directed synthesis algorithm for generating lenses in this
%%   language from regular expressions describing the data formats. A significant
%%   technical challenge in this work arises from the fact that our target language
%%   permits synchronization between formats that don't have exactly the same data
%%   -- data in one format need not be present in the other format. This gives the
%%   synthesis algorithm much more freedom, as data can be completely unaligned
%%   (edits in one format are never propagated), completely aligned (the formats
%%   are in bijective correspondence), or anywhere in between. Under the assumption
%%   that users typically want to align as much data as possible, we provide an
%%   information theoretic metric for how much data is left unaligned based on the
%%   theory of \emph{stochastic regular expressions}. Furthermore, we use this
%%   metric to develop a greedy synthesis algorithm that tries to minimize
%%   unaligned data. We experimentally demonstrate that our algorithm can
%%   efficiently synthesize simple symmetric lenses on a variety of benchmark
%%   suites consisting of synchronizing file formats from configuration files,
%%   application-specific data storage files, and data cleaning tasks.
TODO: abstract

>>>>

%% \bcp{This bit feels more detailed / technical than needed for an abstract.}
%%   We develop a type-directed synthesis algorithm for generating lenses in this
%%   language from regular expressions describing the data formats. A significant
%%   technical challenge in this work arises from the fact that our target language
%%   permits synchronization between formats that don't have exactly the same data
%%   -- data in one format need not be present in the other format. This gives the
%%   synthesis algorithm much more freedom, as data can be completely unaligned
%%   (edits in one format are never propagated), completely aligned (the formats
%%   are in bijective correspondence), or anywhere in between. Under the assumption
%%   that users typically want to align as much data as possible, we provide an
%%   information theoretic metric for how much data is left unaligned based on the
%%   theory of \emph{stochastic regular expressions}. Furthermore, we use this
%%   metric to develop a greedy synthesis algorithm that tries to minimize
%%   unaligned data. We experimentally demonstrate that our algorithm can
%%   efficiently synthesize simple symmetric lenses on a variety of benchmark
%%   suites consisting of synchronizing file formats from configuration files,
%%   application-specific data storage files, and data cleaning tasks.

(The idea of lenses.  Their usefulness and popularity.)

Recent work by~\citet{miltner+:bijective-synthesis} has also demonstrated
how techniques from {\em type-directed program synthesis} can be used to
efficiently synthesize the simplest class of lenses: so-called {\em
  bijective lenses}, where no information is discarded when transforming
data in either direction.

We show here how to extend this algorithm to a much richer class of lenses,
which we call {\em simple symmetric lenses}; this class includes all
bijective and standard ``asymmetric'' lenses~\cite{OriginalFosterPOPLpaper},
as well as a rich subset of the full-blown ``symmetric lenses'' studied by
\citet{symmetric-lenses}.

(why our algorithm is harder; how we use information theory to help)
